QPLIB: A Library of Quadratic Programming Instances

### 2017-01-28 QPLIB-2.2.tex
update classification count tables
- reflect current set of instances
- regard objective sense for D and C category

Our taxonomy is based on a three-fields code of the form ``\textit{OVC}'', where \textit{O} indicates the objective function, \textit{V} the variables, and \textit{C} the constraints of the problem. The fields can be given the following values:
%
\begin{itemize}
 \item objective function: (L)inear, (D)iagonal convex quadratic, (C)onvex quadra-tic, nonconvex (Q)uadratic;
 %
 \item variables: (C)ontinuous only, (B)inary only, (M)ixed binary and continuous, (I)nteger only, (G)eneral (all other cases);
 %
 \item constraints: (N)one, (B)ox, (L)inear, (D)iagonal convex quadratic, (C)onvex quadratic, nonconvex (Q)uadratic.
\end{itemize}
%
The wildcard ``*'' will be used to indicate any possible choice, and lists of the form ``\{X, Y, Z\}'' will indicate that the value of the given field can freely attain any of the specified values.

>>>>

Our taxonomy is based on a three-fields code of the form ``\textit{OVC}'', where \textit{O} indicates the objective function, \textit{V} the variables, and \textit{C} the constraints of the problem. The fields can be given the following values:
%
\begin{itemize}
 \item objective function: (L)inear, (D)iagonal convex (if minimization) or concave (if maximization) quadratic, (C)onvex (if minimization) or (C)oncave (if maximization) quadratic,  (Q)uadratic (all other cases);
 %
 \item variables: (C)ontinuous only, (B)inary only, (M)ixed binary and continuous, (I)nteger (incl.\ binary) only, (G)eneral (all other cases);
 %
 \item constraints: (N)one, (B)ox, (L)inear, (D)iagonal convex quadratic, (C)onvex quadratic, nonconvex (Q)uadratic.
\end{itemize}
%
The wildcard ``*'' will be used to indicate any possible choice, and lists of the form ``\{X, Y, Z\}'' will indicate that the value of the given field can freely attain any of the specified values.

### 2017-01-28 QPLIB-3.tex
update classification count tables
- reflect current set of instances
- regard objective sense for D and C category

\begin{center}
\begin{table}
 \centering
 %\scriptsize
 \setlength{\tabcolsep}{18pt}
 \renewcommand \arraystretch{1.1}
\begin{tabular}{lllr}
\toprule
Obj. Fun. & Variables & Constraints & \#\\
\cmidrule(lr){1-4}
%
\multirow{5}*{Linear}
          & \multirow{1}*{Binary}
%                    & None      &   \\
%          &         & Linear    &  \\
                    & Quadratic &   9 \\[1.2 ex]
\cmidrule(lr){2-4}
          & \multirow{2}*{Mixed}
                    & Convex    &   2\\[1.2 ex]
          &         & Quadratic &    118\\[1.2 ex]
\cmidrule(lr){2-4}
          & \multirow{1}*{Integer}
%                    & Linear    &    \\
                   & Quadratic &    2\\[1.2 ex]
\cmidrule(lr){2-4}
          & \multirow{1}*{General}
%                    & Linear    &    \\
                   & Quadratic &    3\\[1.2 ex]
\cmidrule(lr){1-4}
%\multirow{5}*{Linear}
%          & Binary  & Quadratic &   9\\
%          & \multirow{2}*{Mixed}
%                    & Convex    &   2\\
%          &         & Quadratic &  118\\
%%          & \multirow{2}*{Integer}
%%                    & Convex    &  15 \\
%%          &         & Quadratic &   5 \\
%          & {General} & Quadratic &   3 \\
%\hline
\multirow{3}*{Convex}
          & Binary  & Linear    &  2 \\[1.2 ex]
\cmidrule(lr){2-4}
          & \multirow{2}*{Mixed}
                    & Linear    &   13\\[1.2 ex]
          &         & Quadratic &    1\\[1.2 ex]
%          & General & Linear    &    \\
%\hline
\cmidrule(lr){1-4}
\multirow{7}*{Quadratic}
          & \multirow{3}*{Binary}
                    & None      &   23\\[1.2 ex]
          &         & Linear    &  59\\[1.2 ex]
          &         & Quadratic &   5 \\[1.2 ex]
\cmidrule(lr){2-4}
          & \multirow{2}*{Mixed}
                    & Linear    &   10\\[1.2 ex]
          &         & Quadratic &    1\\[1.2 ex]
%          & Integer & Linear    &    \\
\cmidrule(lr){2-4}
          & \multirow{1}*{Integer}
                    & Linear    &    2\\[1.2 ex]
\cmidrule(lr){2-4}
          & \multirow{1}*{General}
                    & Quadratic    &    1\\[1.2 ex]
%          &         & Quadratic &    \\
\hline
Total     &         &           & 251\\
%
\bottomrule
\end{tabular}
\caption{Classification of the final set of discrete instances}
\label{tab:DD}
\end{table}
\end{center}

\begin{center}
\begin{table}
 \centering
 %\scriptsize
 \setlength{\tabcolsep}{18pt}
 \renewcommand \arraystretch{1.1}
\begin{tabular}{llr}
\toprule
Obj. Fun. & Constraints & \#\\
\cmidrule(lr){1-3}
%
\multirow{2}*{Linear}    & Convex    &   11\\[1.2 ex]
                         & Quadratic &   50\\[1.2 ex]
\cmidrule(lr){1-3}
\multirow{4}*{Convex}
                         & Box       &   3 \\[1.2 ex]
                         & Linear    &   12\\[1.2 ex]
                         & Convex    &    2\\[1.2 ex]
                         & Quadratic &    5\\[1.2 ex]
\cmidrule(lr){1-3}
\multirow{3}*{Quadratic}
                         & Linear    &   5\\[1.2 ex]
                         & Convex    &   11\\[1.2 ex]
                         & Quadratic &   17\\[1.2 ex]
\hline
Total                    &           & 116 \\
%
\bottomrule
\end{tabular}
\caption{Classification of the final set of continuous instances}
\label{tab:CC}
\end{table}
\end{center}

>>>>

\begin{table}
 \centering
 %\scriptsize
 \setlength{\tabcolsep}{18pt}
 \renewcommand \arraystretch{1.1}
\begin{tabular}{lllr}
\toprule
Obj. Fun. & Variables & Constraints & \#\\
\cmidrule(lr){1-4}
%
\multirow{5}*{Linear}
          & \multirow{1}*{Binary}
%                    & None      &   \\
%          &         & Linear    &  \\
                    & Quadratic &   9 \\[1.2 ex]
\cmidrule(lr){2-4}
          & \multirow{2}*{Mixed}
                    & Convex    &   2\\[1.2 ex]
          &         & Quadratic &    118\\[1.2 ex]
\cmidrule(lr){2-4}
          & \multirow{1}*{Integer}
%                    & Linear    &    \\
                   & Quadratic &    2\\[1.2 ex]
\cmidrule(lr){2-4}
          & \multirow{1}*{General}
%                    & Linear    &    \\
                   & Quadratic &    3\\[1.2 ex]
\cmidrule(lr){1-4}
%\multirow{5}*{Linear}
%          & Binary  & Quadratic &   9\\
%          & \multirow{2}*{Mixed}
%                    & Convex    &   2\\
%          &         & Quadratic &  118\\
%%          & \multirow{2}*{Integer}
%%                    & Convex    &  15 \\
%%          &         & Quadratic &   5 \\
%          & {General} & Quadratic &   3 \\
%\hline
\multirow{1}*{Convex (if min)}
          & Binary  & Linear    &  2 \\[1.2 ex]
\cmidrule(lr){2-4}
\multirow{1}*{or}
          & \multirow{2}*{Mixed}
                    & Linear    &   14\\[1.2 ex]
\multirow{2}*{Concave (if max)}
          &         & Quadratic &    1\\[1.2 ex]
%          & General & Linear    &    \\
\cmidrule(lr){2-4}
          & \multirow{1}*{Integer}
                    & Linear    &   2\\[1.2 ex]
%\hline
\cmidrule(lr){1-4}
\multirow{6}*{Quadratic}
          & \multirow{3}*{Binary}
                    & None      &   23\\[1.2 ex]  % there are actually QBB due to the {0,1} bounds on the binary variables
          &         & Linear    &  59\\[1.2 ex]
          &         & Quadratic &   5 \\[1.2 ex]
\cmidrule(lr){2-4}
          & \multirow{2}*{Mixed}
                    & Linear    &   9\\[1.2 ex]
          &         & Quadratic &    1\\[1.2 ex]
%          & Integer & Linear    &    \\
\cmidrule(lr){2-4}
          & \multirow{1}*{General}
                    & Quadratic    &    1\\[1.2 ex]
%          &         & Quadratic &    \\
\hline
Total     &         &           & 251\\
%
\bottomrule
\end{tabular}
\caption{Classification of the final set of discrete instances}
\label{tab:DD}
\end{table}

\begin{table}
 \centering
 %\scriptsize
 \setlength{\tabcolsep}{18pt}
 \renewcommand \arraystretch{1.1}
\begin{tabular}{llr}
\toprule
Obj. Fun. & Constraints & \#\\
\cmidrule(lr){1-3}
%
\multirow{2}*{Linear}    & Convex    &   15\\[1.2 ex]
                         & Quadratic &   46\\[1.2 ex]
\cmidrule(lr){1-3}
\multirow{1}*{Convex (if min)}
                         & Box       &   3 \\[1.2 ex]
\multirow{1}*{or}
                         & Linear    &   11\\[1.2 ex]
                        % & Convex    &    2\\[1.2 ex]
\multirow{1}*{Concave (if max)}
                         & Quadratic &    9\\[1.2 ex]
\cmidrule(lr){1-3}
\multirow{3}*{Quadratic}
                         & Linear    &   6\\[1.2 ex]
                         & Convex    &   1\\[1.2 ex]
                         & Quadratic &   25\\[1.2 ex]
\hline
Total                    &           & 116 \\
%
\bottomrule
\end{tabular}
\caption{Classification of the final set of continuous instances}
\label{tab:CC}
\end{table}
